A White Noise Approach to Evolutionary Ecology

### 2020-04-12 .A White Noise Approach To Evolutionary Ecology/draft.Rmd
classical solutions

Set 
\begin{equation}
\Phi(x,t)=\frac{\exp\left(-x^2/2\mu t\right)}{\sqrt{2\pi\mu t}}.
\end{equation}
Then the semigroup $\{S(t)\}_{t\geq0}$ given by 
\begin{equation}
S(t)v=\left\{\begin{matrix}
\int_0^t\frac{\mu}{2}\Delta\nu(x,s)ds=\int_\mathbb{R}\Phi(x-y,t)v(y)dy, & t>0 \\
 & \\
v, &t=0
\end{matrix}\right.
\end{equation}
for all $v\in L^\infty(\mathbb{R})$ satisfies $\|S(t)v\|_1=\|v\|_1$ for all $t\geq0$ and $v\in L^1(\mathbb{R})$. We also define the operator
\begin{equation}
(Fv)(x)=m\left(\int_\mathbb{R}\kappa(x-y)v(y)dy,x\right)v(x), \ \ \forall \ \ v\in L^1(\mathbb{R}).
\end{equation}
Thus $\|Fv\|_1\leq |r| \ \|v\|_1$ for all $v\in L^1(\mathbb{R})$ which implies $F$ is Lipschitz continuous. For $T>0$ set $L^{\infty,1}([0,T]\times\mathbb{R})$ as the set of functions $\nu:[0,T]\to L^1(\mathbb{R})$ that satisfy $\|\nu\|_{1,T}=\sup_{t\in[0,T]}\|\nu(t)\|_1<+\infty$ and consider the operator $G$ defined on $L^{\infty,1}([0,T]\times\mathbb{R})$ for fixed $u\in L^1(\mathbb{R})$ by
\begin{equation}
(Gv)(t)=S(t)u+\int_0^tS(t-s)(Fv(s))ds \ \ \forall \ \ t\in[0,T].
\end{equation}
Then for any $t\in[0,T]$ and $\nu_1,\nu_2\in L^{\infty,1}([0,T]\times\mathbb{R})$,

@@

We shift our focus to showing mild solutions $\nu$ to PDE (\ref{PDE_supp}) are twice differentiable in $x$ and hence are classical solutions. Applying lemma 3.3.2 of Henry [-@Henry1981] we have that the mild solution $\nu$ is in fact a strong (but necessarily classical) solution to the Cauchy problem defined by PDE (\ref{PDE_supp}) with initial condition $\nu(0)=u$ for $t\in[0,T]$. In particular, this implies that $\nu(t)\in D(\Delta)$ for each $t\in(0,T)$ where $D(\Delta)=W^{2,1}(\mathbb{R})$ is the Sobolov space of integrable functions with weak derivatives at least of order $2$. Since $\frac{1}{p}\geq\frac{1}{p+1}\geq\frac{1}{p}-2$ for all $p\geq1$, the Sobolov embedding theorem [@Henry1981] implies $D(\Delta)\subset L^p(\mathbb{R})$, the Lebesgue space of $p$-integrable functions on $\mathbb{R}$, for all $p\geq1$. Hence $D(\Delta)\subset W^{2,p}(\mathbb{R})$, the Sobolov space of $p$-integrable functions with weak derivatives at least of order $2$, for all $p\geq1$.

>>>>

Set 
\begin{equation}
\Phi(x,t)=\frac{\exp\left(-x^2/2\mu t\right)}{\sqrt{2\pi\mu t}}.
\end{equation}
Then the semigroup $\{S(t)\}_{t\geq0}$ given by 
\begin{equation}
S(t)v=\left\{\begin{matrix}
\int_0^t\frac{\mu}{2}\Delta\nu(x,s)ds=\int_\mathbb{R}\Phi(x-y,t)v(y)dy, & t>0 \\
 & \\
v, &t=0
\end{matrix}\right.
\end{equation}
for all $v\in L^\infty(\mathbb{R})$ satisfies $\|S(t)v\|_1=\|v\|_1$ for all $t\geq0$ and $v\in L^1(\mathbb{R})$. We also define the operator
\begin{equation}
(Fv)(x)=m\left(\int_\mathbb{R}\kappa(x-y)v(y)dy,x\right)v(x), \ \ \forall \ \ v\in L^1(\mathbb{R}).
\end{equation}
Thus $\|Fv\|_1\leq |r| \ \|v\|_1$ for all $v\in L^1(\mathbb{R})$. Then, for any $v,w\in L^1(\mathbb{R})$,
\begin{multline}
Fv-Fw=F(v+w)-F(v+w)+Fv-Fw \\
=m(v+w,x)(v+w)-m(w,x)w-m(v+w,x)(v+w)+m(v,x)v \\
=\Big(m(v+w,x)-m(w,x)\Big)w-\Big(m(v+w,x)-m(v,x)\Big)v+m(v+w,x)(v-w).
\end{multline}
Hence $\|Fv-Fw\|_1\leq2|r|(\|w\|_1+\|v\|_2)+|r|\|v-w\|_1\leq\|r\|\|v-w\|_1$ which implies $F$ is Lipschitz continuous on $L^1(\mathbb{R})$. For $T>0$ set $L^{\infty,1}([0,T]\times\mathbb{R})$ as the set of functions $\nu:[0,T]\to L^1(\mathbb{R})$ that satisfy $\|\nu\|_{1,T}=\sup_{t\in[0,T]}\|\nu(t)\|_1<+\infty$ and consider the operator $G$ defined on $L^{\infty,1}([0,T]\times\mathbb{R})$ for fixed $u\in L^1(\mathbb{R})$ by
\begin{equation}
(Gv)(t)=S(t)u+\int_0^tS(t-s)(Fv(s))ds \ \ \forall \ \ t\in[0,T].
\end{equation}
Then for any $t\in[0,T]$ and $\nu_1,\nu_2\in L^{\infty,1}([0,T]\times\mathbb{R})$,

@@

We shift our focus to showing mild solutions $\nu$ to PDE (\ref{PDE_supp}) are twice differentiable in $x$ and hence are classical solutions. Applying lemma 3.3.2 of Henry [-@Henry1981] we have that the mild solution $\nu$ is in fact a strong solution (i.e., differentiable with respect to $t\in(0,T)$) to the abstract Cauchy problem defined by PDE (\ref{PDE_supp}) with initial condition $\nu(0)=u$ for $t\in[0,T]$. In particular, this implies that $\nu(t)\in D(\Delta)$ for each $t\in(0,T)$ where $D(\Delta)=W^{2,1}(\mathbb{R})$ is the Sobolov space of integrable functions with weak derivatives at least of order $2$. Since $\frac{1}{p}\geq\frac{1}{p+1}\geq\frac{1}{p}-2$ for all $p\geq1$, the Sobolov embedding theorem [@Henry1981] implies $D(\Delta)\subset L^p(\mathbb{R})$, the Lebesgue space of $p$-integrable functions on $\mathbb{R}$, for all $p\geq1$. Hence $D(\Delta)\subset W^{2,p}(\mathbb{R})$, the Sobolov space of $p$-integrable functions with weak derivatives at least of order $2$, for all $p\geq1$.
